Formal Grammars as Types in Non-Commutative Linear-Non-Linear Type Theory

### 2024-07-10 POPL/paper.tex
future/related work stubs

% -*- fill-column: 80; -*-
\documentclass[sigconf,anonymous,review,screen,acmsmall]{acmart}
\usepackage{mathpartir}
\usepackage{tikz-cd}
\usepackage{lipsum}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{fancyvrb}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{stmaryrd}
\usepackage{scalerel}
\usepackage{tikz}
\usetikzlibrary{automata, positioning, arrows, fit}

@@

%% That paper with Fritz Henglein about regexes as types

%% Vaughan Pratt on the residual operator
%%

@@

>>>>

% -*- fill-column: 80; -*-
\documentclass[sigconf,review,anonymous,screen,acmsmall]{acmart}
\usepackage{mathpartir}
\usepackage{tikz-cd}
\usepackage{lipsum}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{fancyvrb}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{stmaryrd}
\usepackage{scalerel}
\usepackage{tikz}
\usetikzlibrary{automata, positioning, arrows, fit}

@@

\steven{Comments from Max or Pedro to mention these:

That paper with Fritz Henglein about regexes as types

Vaughan Pratt on the residual operator

}

\steven{Mention Vakar's ``Syntax and Semantics of Linear Dependent Types'' as
  related work?}

@@

\steven{Rework future work}
\steven{Mention the two-level linear,dependent compiler. ``A two level linear
  dependent type theory''. it could be a good place to build off for a language
  implementation that isn't just inference rules}
